\documentclass[12pt]{article}
\title{EE351K Homework 7}
\author{Hershal Bhave (hb6279)}
\date{Due October 23, 2014}

\usepackage{multicol}
\usepackage[in]{fullpage}
\usepackage{xcolor}
\usepackage{rotating}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{graphics}
\usepackage{caption}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[nosolutionfiles]{answers}
\usepackage[acronym]{glossaries}

\newenvironment{Ex}{\textbf{Problem}\vspace{.75em}\\}{}
\Newassociation{solution}{Soln}{Answers}
\pagebreak[3]
\newcommand{\Opentesthook}[2]{\Writetofile{#1}{\protect\section{#1: #2}}}
\renewcommand{\Solnlabel}[1]{\textbf{Solution}\quad}

\newcommand{\dd}[1]{\:\mathrm{d}{#1}}
\newcommand{\ddt}[1]{\frac{\dd{}}{\dd{#1}}}
\newcommand{\dddt}[1]{\frac{\dd{}^2}{\dd{#1}^2}}

\begin{document}
\maketitle
\begin{enumerate}
\item
  \begin{Ex}
    $X$ and $Y$ are two independent exponential random variables with
    parameters $\lambda_1$ and $\lambda_2$ respectively. Let $Z$ be a
    random variable defined as $Z = \text{max}[X,Y]$; find the
    distribution of $Z$.
    \begin{solution} \hfill \vspace{.75em} \\
      \begin{equation}
        \label{eq:1-sol}
        \begin{aligned}
          F_Z(z) &= P(\text{max}[X,Y] \le z) \\
          &= P(X \le z, Y \le z) \\
          &= P(X\le z)P(Y\le z) \\
          &= (1-e^{-\lambda_1 z})(1-e^{-\lambda_2 z}) \\
          &= 1-e^{-\lambda_1 z} - e^{-\lambda_2 z} + e^{-(\lambda_1 +
            \lambda_2) z} \\
          &= (1 - e^{-\lambda_1 z}) + (1 - e^{-\lambda_2 z})+ (-1 +
          e^{-(\lambda_1 + \lambda_2) z}) \\
          &= (1-e^{-\lambda_1 z}) + (1-e^{-\lambda_2 z}) -
          (1-e^{-(\lambda_1 + \lambda_2) z}) \\
          \implies Z &\sim \text{exp}(\lambda_1) + \text{exp}(\lambda_2)
          - \text{exp}(\lambda_1 + \lambda_2) \\
          \text{Or }\implies Z &\sim
          \text{exp}(\lambda_1)\text{exp}(\lambda_2) \\
        \end{aligned}
      \end{equation}
    \end{solution}
  \end{Ex}
\pagebreak[4]
\item
  \begin{Ex}
    Let $X$ be a continuous random variable with CDF $F_X(x)$ which is
    strictly increasing and $Y$ be a derived random variable defined
    as $Y = F_X(X)$. Find the distribution of $Y$.  Note that CDF of
    any given random variable is just another function.
    \begin{solution} \hfill \vspace{.75em} \\
      \begin{equation}
        \label{eq:2-presol}
        \begin{aligned}
          F_Y(y) &= P(Y\le y) = P(F_X(x)\le y) \\
          &= \int_{\{x|F_X(X) \le y\}}f_X(x) \dd{x} \\
        \end{aligned}
      \end{equation}
      The distribution is then the derivative of the CDF of $Y$.
      \begin{equation}
        \label{eq:2-sol}
        % \implies f_Y(y) = \frac{d}{\dd{y}}\int_{\{x|F_X(X) \le
        %   y\}}f_X(x) \dd{x}
        \implies f_Y(y) = f_X(h(y)) \left|\frac{\dd{h}}{\dd{y}}(y)\right|
      \end{equation}
    \end{solution}
  \end{Ex}
\item
  \begin{Ex}
    Let $X$ be a discrete random variable with PMF $p_X$ and let $Y$
    be a continuous random variable, independent from $X$, with PDF
    $f_Y$. Derive a formula for the PDF of the random variable $X+Y$.
    \begin{solution} \hfill \vspace{.75em} \\
      \begin{equation}
        \label{eq:3-presol}
        \begin{aligned}
          F_Z(z) &= P(Z \le z) = P(X+Y \le z) \\
          &= \sum_x P(X+Y\le z | X=x)p_X(x) \\
          &= \sum_x P(Y \le z-x | X=x)p_X(x) \\
          &= \sum_x P(Y \le z-x)p_X(x) \\
          &= \sum_x F_Y(z-x)p_X(x) \\
        \end{aligned}
      \end{equation}
      Then the distribution of $Z$ is the derivative of its CDF
      \begin{equation}
        \label{eq:3-sol}
        \begin{aligned}
          f_Z(z) &= \frac{d}{\dd{z}}F_Z(z) \\
          &= \frac{d}{\dd{z}}\sum_{x}F_Y(z-x)p_X(x) \\
          &= \sum_{x}\frac{d}{\dd{z}}F_Y(z-x)p_X(x) \\
          \implies f_Z(z) &= \sum_{x}f_Y(z-x)p_X(x) \\
        \end{aligned}
      \end{equation}
    \end{solution}
  \end{Ex}
\item
  \begin{Ex}
    A random variable $X$ has mean 0 and variance 1. A random variable
    $Y$ has mean 1 and variance 2, and $X$ and $Y$ are
    independent. Suppose random variables $U$ and $V$ are given by
    $U=X+2Y$, $V = X-Y$. What is the covariance $\text{Cov}(U,V)$?
    What is the correlation coefficient $\rho_{U,V}$? Can $U$ and $V$
    be independent?
    \begin{solution} \hfill \vspace{.75em} \\
      The covariance formula is
      \begin{equation}
        \label{eq:4-cov}
        \text{Cov}(U,V) = E[UV] - E[U]E[V]
      \end{equation}
      We must first obtain each component of the covariance formula:
      \begin{equation}
        \label{eq:4-e-u}
        \begin{aligned}
          E[U] &= E[X+2Y] \\
          &= E[X] + 2E[Y] \\
          \implies E[U] &= 2 \\
        \end{aligned}
      \end{equation}
      and
      \begin{equation}
        \label{eq:4-e-v}
        \begin{aligned}
          E[V] &= E[X]-E[Y] \\
          &= 0-1 \\
          \implies E[V] &= -1 \\
        \end{aligned}
      \end{equation}
      and
      \begin{equation}
        \label{eq:4-e-uv}
        \begin{aligned}
          E[UV] &= E[(X+2Y)(X-Y)] \\
          &= E[X^2] - E[XY] + E[2XY] - E[2Y^2] \\
          &= E[X^2] + E[XY] - 2E[Y^2] \\
        \end{aligned}
      \end{equation}
      Where $E[X^2]$ and $E[Y^2]$ can be found by
      \begin{multicols}{2}
        \begin{equation}
          \label{eq:4-x-2}
          \begin{aligned}
            \text{Var}(X) &= E[X^2] - E[X]^2 \\
            E[X^2] &= \text{Var}(X) + E[X]^2 \\
            &= 1 + 0^2 \\
            \implies E[X^2] &= 1 \\
          \end{aligned}
        \end{equation} &
        \begin{equation}
          \label{eq:4-y-2}
          \begin{aligned}
            \teyt{Var}(Y) &= E[Y^2] - E[Y]^2 \\
            E[Y^2] &= \teyt{Var}(Y) + E[Y]^2 \\
            &= 2 + 1^2 \\
            \implies E[Y^2] &= 3 \\
          \end{aligned}
        \end{equation}
      \end{multicols}
      Continuing \cref{eq:4-e-uv}
      \begin{equation}
        \label{eq:4-e-uv-cont}
        \begin{aligned}
          E[UV] &= E[X^2] + E[XY] - 2E[Y^2] \\
          &= 1 + 0 - 6 \\
          \implies E[UV] &= -5 \\
        \end{aligned}
      \end{equation}
      Using the individual components found in
      \cref{eq:4-e-u,eq:4-e-v,eq:4-e-uv}, we can find the covariance
      using \cref{eq:4-cov}
      \begin{equation}
        \label{eq:4-cov-plugged}
        \begin{aligned}
          \text{Cov}(U,V) &= E[UV] - E[U]E[V] \\
          &= -5 - (2)(-1) \\
          \implies \text{Cov}(U,V) &= -3 \\
        \end{aligned}
      \end{equation}
      The correlation coefficient is
      \begin{equation}
        \label{eq:4-c-coef}
        \rho(U,V) =
        \frac{\text{Cov}(U,V)}{\sqrt{\text{Var}(U)\text{Var}(V)}}
      \end{equation}
      Where the variances for $U$ and $V$ are found by
      \begin{multicols}{2}
        \begin{equation}
          \label{eq:4-var-u}
          \begin{aligned}
            \text{Var}(U) &= \text{Var}(X) + 4\text{Var}(Y) \\
            \implies \text{Var}(U) &= 9 \\
          \end{aligned}
        \end{equation} &
        \begin{equation}
          \label{eq:4-var-v}
          \begin{aligned}
            \text{Var}(V) &= \text{Var}(X) + \text{Var}(Y) \\
            \implies \text{Var}(V) &= 3 \\
          \end{aligned}
        \end{equation}
      \end{multicols}
      Plugging these values in \cref{eq:4-c-coef}, we obtain
      \begin{equation}
        \label{eq:4-c-coef-plugged}
        \begin{aligned}
          \rho(U,V) &= \frac{-3}{\sqrt{(3)(9)}} \\
          \implies \rho(U,V) &= \frac{1}{\sqrt{3}} \\
        \end{aligned}
      \end{equation}
      Since $\text{Cov}(U,V)$ is not zero, $U$ and $V$ are definitely
      not independent.
    \end{solution}
  \end{Ex}
\item
  \begin{Ex}
    Consider $n$ independent tosses of a $k$-sided fair die. Let $X_i$
    be the number of tosses that result in outcome $i$. Find
    $\text{Cov}(X_1 , X_2)$ of $X_1$ and $X_2$.

    Hint: Define a Bernoulli random variable $A_t$ that is equal to 1
    if and only if the $t$th toss resulted in 1. Note that $X_1 =
    A_1+A_2+\ldots+A_n$.
    \begin{solution} \hfill \vspace{.75em} \\
      Let's start by defining a few variables:
      \begin{equation}
        \label{eq:5-decl}
        \begin{aligned}
          X_1 &= A_1+A_2+\ldots+A_n \\
          X_2 &= B_1+B_2+\ldots+B_n \\
        \end{aligned}
      \end{equation}
      Where $A_t$ and $B_t$ are Bernoilli randomm variables which are
      1 when only if the $t$th toss is equal to $i$ for a random
      variable $X_i$. Now
      \begin{equation}
        \label{eq:5-e-0}
        E[X_1X_2] = E[(A_1 + \ldots + A_n)(B_1 + \ldots + B_n)]
      \end{equation}
      By the binomial theorem,
      \begin{equation}
        \label{eq:5-e-1}
        \begin{aligned}
          E[X_1X_2] & = E[(A_1 + \ldots + A_n)(B_1 + \ldots + B_n)] \\
          &= \frac{n(n-1)}{k^2} \\
        \end{aligned}
      \end{equation}
      The covarance can be found by
      \begin{equation}
        \label{eq:5-sol}
        \begin{aligned}
          \text{Cov}(X_1, X_2) &= E[X_1X_2] - E[X_1]E[X_2] \\
          &= \frac{n(n-1)}{k^2} - \frac{n^2}{k^2} \\
          \implies \text{Cov}(X_1, X_2) &= -\frac{n}{k^2}
        \end{aligned}
      \end{equation}
    \end{solution}
  \end{Ex}
\item
  \begin{Ex}
    Let c be an integer where $c > 1$. We are given $c$ independent
    random variables, denoted $X_1, \ldots ,X_c$ and $c$ positively
    correlated random variables, denoted by $Y_1, \ldots, Y_c$ such
    that correlation between any two random variables $Y_i$ and $Y_j$
    is a constant value $\rho < 1$. All the given random variables
    have same mean and variance.
    \begin{enumerate}
    \item Which of the following has a lower variance?
      \begin{equation}
        \label{eq:6-question-eq-0}
        \text{Var}(X_1 + X_2 + \cdots + X_c)
      \end{equation}
      \begin{equation}
        \label{eq:6-question-eq-1}
        \text{Var}(Y_1 + Y_2 + \cdots + Y_c)
      \end{equation}
      \begin{equation}
        \label{eq:6-question-eq-2}
        \text{Var}(cX_1)
      \end{equation}
      Compute each of these to relate them.
    \item Suppose each random variable denotes an investment in a
      given stock. Consider the following cases, investing $c$ times
      in a single stock, investing in $c$ independent stocks and
      investing in $c$ positively correlated stocks. Which investement
      is involved with less risk? Explain your answer using the result
      to the previous question.
    \end{enumerate}
    \begin{solution} \hfill
      \begin{enumerate}
      \item
        In general,
        \begin{equation}
          \label{eq:6-variance-sum}
          \text{Var}\left(\sum_{i=1}^{n}X_i\right) =
          \left(\sum_{i=1}^{n}\text{Var}(X_i)\right) +
          \left(\sum_{\{(i,j)|i\not= j\}}^{n}\text{Cov}(X_i, X_j)\right)
        \end{equation}
        and
        \begin{equation}
          \label{eq:6-rho}
          \begin{aligned}
            \rho &=
            \frac{\text{Cov}(X,Y)}{\sqrt{\text{Var}(X)\text{Var}(Y)}}
            \\
            \implies \text{Cov}(X,Y) &=
            \rho\sqrt{\text{Var}(X)\text{Var}(Y)} \\
          \end{aligned}
        \end{equation}
        The lowest value is for \cref{eq:6-question-eq-0}.
      \item
        We would want the least risky investment, which has $c$
        independent options, which corresponds to
        \cref{eq:6-question-eq-0}.
      \end{enumerate}
    \end{solution}
  \end{Ex}
\item
  \begin{Ex}
    Let $X$ be a random variable uniformly distributed between −0.5
    and 0.5 and $q$ be a uniform quantizer function with resolution of
    $n$ bits. If $n = 2$, the quantizer function is shown below.

    {\huge SHOW QUANTIZER FUNCTION}

    Let $Y = q(X)$ be a derived random variable. Random variable $Y$
    takes four values for $n = 2$, where each value will be associated
    with two bits. SNR is used as a measure of quality for the
    quantizer and is defined as $$\text{SNR} = \sigma_X^2
    E[(X−q(X))^2]$$ Find SNR for $n=2$. SNR in db is defined as
    $\text{SNR}_{\text{db}} = 10\log 10\;\text{SNR}$ .What happens to
    $\text{SNR}_{\text{db}}$ as number of bits, $n$ increases?

    \begin{solution} \hfill \vspace{.75em} \\
      {\huge TODO}
    \end{solution}
  \end{Ex}

\end{enumerate}
\end{document}
